Inferring generation-interval distributions from contact tracing data

### 2018-09-26 doc/network.tex
tweak

\swp{I might say something about independence transmission events in the results -- see forsberg 2008...}

First, we compared the four methods by simulating a stochastmic epidemic model homogeneous network with 100000 individuals using Ebola-like parameters for 15 weeks (Figure~?).

>>>>

\swp{I might say something about independence transmission events in the results if I decide to compare forsberg2008 as well -- see forsberg 2008...}

We compare how the estimates from the two methods vary across time using a single stochastic simulation on a homogeneous network (Figure~\ref{fig:example}).
During the initial exponential growth period (approximately between 9 and 20 weeks), both nonparametric and parametric methods yield similar estimates of mean generation interval and reproductive number.
Howeve, we observe opposite trends after the growth period (approximately after 20 weeks).
As the nonparametric method takes a weighted average of the observed distribution, increase in the observed mean generation interval leads to increase in the nonparametric estimates of both mean generation interval and reproductive number.
On the other hand, as the parametric method assumes a Poisson process with constant proportion of susceptibles, decrease in the number of susceptible results in underestimation of both mean generation interval and reproductive number.
we observe grdaual increase in the observed mean-generation interval as we aggregate more data, but the observed estimates always underestimate both mean generation interval and reproductive number, as predicted from the deterministic simulations.

\begin{figure}
\includegraphics[width=\textwidth]{../fig/example.pdf}
\caption{Fill this out.}
\label{fig:example}
\end{figure}

Then, we compare accuracy and reliability of the two methods during the initial growth period using 100 stochastic simulations on a homogeneous network (Figure~\ref{fig:test}).
We find that the parametric method provides the most consistent (least variable) estimates.
The nonparametric method overestimates reproductive number initially but this is likely driven by the initial overestimation of the growth rate (Figure~\ref{fig:example}).

\swp{May need to explain coverage...}
Surprisingly, both methods fail to reach nominal coverage.

\begin{figure}
\includegraphics[width=\textwidth]{../fig/compare_methods.pdf}
\caption{Fill this out.}
\label{fig:test}
\end{figure}
